### 2024-03-17 thesis/sections/5.3-reference-resolution.tex
results

\subsubsection*{Results}
Tables \ref{tab:results:reference-resolver} to \ref{tab:results:reference-resolver-masked} show the results of the five adaptions of the reference resolver.
Across the first three models (basic reference resolver, +one-hot, +one-hot+locations), the same patterns can be seen.

>>>>

\subsubsection*{Results}
\cmtDK[inline]{attention predictor}

Tables \ref{tab:results:reference-resolver} to \ref{tab:results:reference-resolver-masked} show the results of the five adaptions of the reference resolver.
Across the first three models (basic reference resolver, +one-hot, +one-hot+locations), the same patterns can be seen.

### 2024-03-17 thesis/sections/6.2-re-generation.tex
results

\subsubsection*{Results}
\begin{table}[ht]
    \centering
    \begin{tabular}{ccc|ccc|ccc}
        \toprule
              &         &         & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                             \\\cmidrule(lr){4-6}\cmidrule(lr){7-9}
        $|V|$ & $h_{s}$ & $h_{r}$ & \textbf{Acc.}                       & \textbf{word-by-word}               & \textbf{length} & \textbf{Acc.} & \textbf{word-by-word} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}    & {22,9\%}                            & {62,8\%}                            & {1}             & {7,1\%}       & {40\%}                & {1}             \\
        {13}  & {10}    & {10}    & {22,8\%}                            & {62,9\%}                            & {0}             & {7,3\%}       & {38,7\%}              & {1}             \\
        {20}  & {10}    & {10}    & {24,6\%}                            & {64\%}                              & {1}             & {6,7\%}       & {38,7\%}              & {1}             \\
        {100} & {10}    & {10}    & {24,4\%}                            & {62\%}                              & {1}             & {7,8\%}       & {40\%}                & {1}             \\
        {100} & {100}   & {100}   & {21\%}                              & {62\%}                              & {1}             & {6,5\%}       & {37,8\%}              & {1}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the caption generator: $|V|$ are different vocabulary sizes and $h$ hidden sizes.}
    % SD: What is word-by-word?
    % DK: the same as in the caption generator with a single model (QUESTION)
    \label{tab:results_caption_generator_game}
\end{table}

>>>>

\subsubsection*{Results}
\begin{table}[ht]
    \centering
    \begin{tabular}{cc|ccc|ccc|ccc}
        \toprule
                                      &        & \multicolumn{3}{c}{\textbf{Dale 2}} & \multicolumn{3}{c}{\textbf{Dale 5}} & \multicolumn{3}{c}{\textbf{CLEVR color}}                                                                                                    \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
        $n$                           & $|V|$  & \textbf{Acc}                        & \textbf{F1}                         & \textbf{NT}                              & \textbf{Acc}     & \textbf{F1}      & \textbf{NT}     & \textbf{Acc} & \textbf{F1} & \textbf{NT} \\\midrule
        \multicolumn{2}{c|}{baseline} & {41,8} & {42,36}                             & {37,11}                             & {62,66}                                  & {81,16}          & {18,36}          & {13,52}         & {33,08}      & {34,53}                   \\\midrule
        {1}                           & {2}    & {70,49}                             & {54,73}                             & {7,29}                                   & {70,16}          & {85,06}          & {13,06}         & {11,68}      & {32,25}     & {34,03}     \\
        {1}                           & {10}   & {78,26}                             & {63,33}                             & {3,56}                                   & {68,97}          & {85,01}          & {10,85}         & {12,72}      & {32,77}     & {33,85}     \\
        {1}                           & {16}   & {74,18}                             & {52,21}                             & {5,38}                                   & {71,57}          & {86,87}          & {10,72}         & {13,19}      & {33,64}     & {33,33}     \\
        {1}                           & {50}   & {70,83}                             & {43,56}                             & {4,21}                                   & {65,23}          & {83,11}          & {12,54}         & {11,81}      & {33,14}     & {34,72}     \\
        {1}                           & {100}  & {73,18}                             & {52,14}                             & {3,86}                                   & {60,94}          & {80,85}          & {20,36}         & {13,67}      & {33,71}     & {33,64}     \\
        {2}                           & {2}    & {72,31}                             & {50,42}                             & {5,52}                                   & {66,2}           & {83,39}          & {14,42}         & {13,32}      & {33,62}     & {32,73}     \\
        {2}                           & {10}   & {75,22}                             & {58,4}                              & {3,99}                                   & {73,22}          & {87,68}          & {9,03}          & {12,37}      & {33,3}      & {34,11}     \\
        {2}                           & {16}   & {\textbf{81,64}}                    & {\textbf{73,66}}                    & {\textbf{2,86}}                          & {73,44}          & {88,21}          & {8,85}          & {12,98}      & {33,94}     & {34,24}     \\
        {2}                           & {50}   & {74,39}                             & {48,53}                             & {3,17}                                   & {\textbf{75,35}} & {\textbf{88,77}} & {\textbf{8,07}} & {14,19}      & {33,04}     & {33,46}     \\
        {2}                           & {100}  & {74,09}                             & {54,88}                             & {3,65}                                   & {54,56}          & {76,95}          & {22,57}         & {13,28}      & {32,8}      & {33,38}     \\
        {3}                           & {2}    & {71,03}                             & {50,76}                             & {4,62}                                   & {65,18}          & {82,68}          & {14,23}         & {12,76}      & {33,58}     & {33,64}     \\
        {3}                           & {10}   & {76,91}                             & {59,42}                             & {2,6}                                    & {71,66}          & {87,14}          & {9,9}           & {12,54}      & {32,75}     & {33,85}     \\
        {3}                           & {16}   & {79,95}                             & {67,55}                             & {3,17}                                   & {50,13}          & {73,24}          & {24,22}         & {12,93}      & {33,79}     & {34,46}     \\
        {3}                           & {50}   & {62,93}                             & {48,03}                             & {16,58}                                  & {\textbf{76,09}} & {\textbf{88,5}}  & {\textbf{9,2}}  & {13,67}      & {33,73}     & {34,29}     \\
        {3}                           & {100}  & {75,74}                             & {57,51}                             & {2,43}                                   & {69,7}           & {86,14}          & {9,38}          & {13,02}      & {33,64}     & {34,2}      \\
        {4}                           & {2}    & {41,23}                             & {42,53}                             & {35,33}                                  & {63,93}          & {82,34}          & {15,3}          & {12,2}       & {33,25}     & {33,64}     \\
        {4}                           & {10}   & {78,99}                             & {66,4}                              & {2,08}                                   & {73,22}          & {88,01}          & {10,85}         & {12,5}       & {33,55}     & {33,16}     \\
        {4}                           & {16}   & {\textbf{80,08}}                    & {\textbf{70,48}}                    & {\textbf{3,47}}                          & {69,4}           & {86,09}          & {10,63}         & {11,72}      & {33,1}      & {34,03}     \\
        {4}                           & {50}   & {75,48}                             & {54,44}                             & {3,34}                                   & {71,35}          & {86,61}          & {10,68}         & {11,81}      & {33,18}     & {34,33}     \\
        {4}                           & {100}  & {74,78}                             & {57,09}                             & {3,86}                                   & {59,2}           & {80,14}          & {20,57}         & {12,67}      & {32,3}      & {34,55}     \\
        {6}                           & {2}    & {72,87}                             & {51,44}                             & {2,78}                                   & {60,82}          & {80,42}          & {17,07}         & {13,45}      & {33,73}     & {33,64}     \\
        {6}                           & {10}   & {73,61}                             & {48,73}                             & {2,82}                                   & {32,64}          & {58,42}          & {33,12}         & {11,89}      & {33,15}     & {35,03}     \\
        {6}                           & {16}   & {73,52}                             & {49,67}                             & {2,43}                                   & {49,39}          & {73,19}          & {23,78}         & {13,06}      & {32,31}     & {34,64}     \\
        {6}                           & {50}   & {44,31}                             & {45,07}                             & {33,29}                                  & {\textbf{78,82}} & {\textbf{90,22}} & {\textbf{7,29}} & {12,72}      & {33,29}     & {32,99}     \\
        {6}                           & {100}  & {\textbf{80,95}}                    & {\textbf{69,88}}                    & {\textbf{3,34}}                          & {62,2}           & {80,62}          & {19,88}         & {14,24}      & {32,36}     & {32,94}     \\
        \bottomrule
    \end{tabular}
    \caption{TODO: caption}
    \label{TODO: label}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{rr|cc|c|ccc|c|c}
        \toprule
                                         &             & {small} & {large} & \textbf{size}  & {cube}  & {cylinder} & {sphere} & \textbf{shape} & {<pad>} \\\midrule
        \multirow{2}{*}{\textbf{Dale-2}} & {Precision} & {45,15} & {37,96} & \textbf{41,56} & {99,25} & {99,65}    & {99,21}  & \textbf{99,37} & {94,58} \\
                                         & {Recall}    & {16,69} & {6,23}  & \textbf{11,46} & {99,59} & {98,55}    & {99,84}  & \textbf{99,33} & {99,3}  \\\midrule
        \multirow{2}{*}{\textbf{Dale-5}} & {Precision} & {80,9}  & {89,63} & \textbf{85,27} & {97,67} & {97,7}     & {95,21}  & \textbf{96,86} & {88,1}  \\
                                         & {Recall}    & {76,99} & {69,14} & \textbf{73,07} & {96,58} & {97,22}    & {96,72}  & \textbf{96,84} & {96,1}  \\\midrule
        \multirowcell{2}[0pt][r]{\textbf{CLEVR}                                                                                                          \\\textbf{color}} & {Precision}  & {-}     & {-}     & \textbf{-}     & {100}   & {100}      & {100}    & \textbf{100}   & {100}   \\
                                         & {Recall}    & {-}     & {-}     & \textbf{-}     & {100}   & {100}      & {100}    & \textbf{100}   & {100}   \\
        \bottomrule
    \end{tabular}
    \caption{Precision and Recall in \% for <pad>, size and shape tokens with $e=100$, $LSTM_o=500$ and $LSTM_e=30$. The columns \textbf{shape} and \textbf{size} show the average across all tokens of the respective attribute.}
    \label{tab:results:bb-re-generator_size-shape}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{rr|cccccccc|c}
        \toprule
                                         &             & {blue}  & {brown} & {cyan}  & {gray}  & {green} & {purple} & {red}   & {yellow} & \textbf{color}   \\\midrule
        \multirow{2}{*}{\textbf{Dale-2}} & {Precision} & {66}    & {79,35} & {71,14} & {86,11} & {70,48} & {70,74}  & {67,95} & {76,26}  & \textbf{73,5}    \\
                                         & {Recall}    & {88,96} & {63,43} & {91,9}  & {46,02} & {69,29} & {65,99}  & {75,35} & {79,54}  & \textbf{72,56}   \\\midrule
        \multirow{2}{*}{\textbf{Dale-5}} & {Precision} & {92,61} & {93,3}  & {94,73} & {91,12} & {93,66} & {88,71}  & {88,04} & {89,79}  & \textbf{91,5}    \\
                                         & {Recall}    & {89,09} & {86,31} & {91,08} & {89,08} & {83,23} & {92,16}  & {93,05} & {88,77}  & {\textbf{89,1}}  \\\midrule
        \multirowcell{2}[0pt][r]{\textbf{CLEVR}                                                                                                             \\\textbf{color}} & {Precision}           & {0} & {0} & {0} & {0} & {12,91} & {13,9}  & {0} & {0}   & \textbf{3,35} \\
                                         & {Recall}    & {0}     & {0}     & {0}     & {0}     & {36,25} & {69,85}  & {0}     & {0}      & {\textbf{13,26}} \\
        \bottomrule
    \end{tabular}
    \caption{Precision and Recall in \% for color tokens with $e=100$, $LSTM_o=500$ and $LSTM_e=30$. The column \textbf{color} shows the average across all colors.}
    \label{tab:results:bb-re-generator_color}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|ccc|ccc|ccc}
        \toprule
                                      &         & \multicolumn{3}{c}{\textbf{Dale 2}} & \multicolumn{3}{c}{\textbf{Dale 5}} & \multicolumn{3}{c}{\textbf{CLEVR colour}}                                                                                                                                                                                                           \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
        $n$                           & $|V|$   & \textbf{A\textsubscript{color}}     & \textbf{A\textsubscript{shape}}     & \textbf{A\textsubscript{size}}            & \textbf{A\textsubscript{color}} & \textbf{A\textsubscript{shape}} & \textbf{A\textsubscript{size}} & \textbf{A\textsubscript{color}} & \textbf{A\textsubscript{shape}} & \textbf{A\textsubscript{size}} \\\midrule
        \multicolumn{2}{c|}{baseline} & {92,03} & {88,91}                             & {50,55}                             & {89,38}                                   & {80,78}                         & {49,92}                         & {90,78}                        & {100}                           & {76,72}                                                          \\\midrule
        {1}                           & {2}     & {93,68}                             & {89,69}                             & {52,04}                                   & {90,12}                         & {88,09}                         & {49,74}                        & {87,37}                         & {100}                           & {76,56}                        \\
        {1}                           & {10}    & {94,21}                             & {96,31}                             & {52,78}                                   & {90,15}                         & {90,6}                          & {49,74}                        & \textbf{91,32}                  & {100}                           & {76,52}                        \\
        {1}                           & {16}    & {92,8}                              & {94,97}                             & {52,78}                                   & {93,45}                         & {91,97}                         & {49,74}                        & {91,03}                         & {100}                           & {76,52}                        \\
        {1}                           & {50}    & {91,58}                             & {90,1}                              & {52,78}                                   & {93,39}                         & {94,66}                         & {49,74}                        & {89,41}                         & {100}                           & {76,52}                        \\
        {1}                           & {100}   & {92,66}                             & {90,41}                             & {52,78}                                   & {90,23}                         & {83,03}                         & {49,74}                        & {86,72}                         & {100}                           & {76,52}                        \\
        {2}                           & {2}     & {92,45}                             & {92,45}                             & {52,04}                                   & \textbf{94,38}                  & {88,72}                         & {49,74}                        & {88,89}                         & {100}                           & {76,56}                        \\
        {2}                           & {10}    & {\textbf{94,44}}                    & {96,09}                             & {52,78}                                   & {90,71}                         & {91,54}                         & {49,74}                        & {89,54}                         & {100}                           & {76,52}                        \\
        {2}                           & {16}    & {92,66}                             & {90,58}                             & {52,78}                                   & {94,14}                         & \textbf{97,18}                  & {49,74}                        & {86,98}                         & {100}                           & {76,52}                        \\
        {2}                           & {50}    & {92,45}                             & {89,28}                             & {52,78}                                   & {93,01}                         & {92,01}                         & {49,74}                        & {86,5}                          & {100}                           & {76,52}                        \\
        {2}                           & {100}   & {92,97}                             & {\textbf{98,91}}                    & {52,78}                                   & {92,49}                         & {92,66}                         & {49,74}                        & {86,68}                         & {100}                           & {76,52}                        \\
        {3}                           & {2}     & {93,32}                             & {90,97}                             & {52,04}                                   & {92,53}                         & {87,88}                         & {49,74}                        & {90,58}                         & {100}                           & {76,56}                        \\
        {3}                           & {10}    & \textbf{{94,79}}                    & {97,01}                             & {52,78}                                   & {92,8}                          & {94,4}                          & {49,74}                        & \textbf{91,17}                  & {100}                           & {76,52}                        \\
        {3}                           & {16}    & {93,1}                              & {95,36}                             & {52,78}                                   & {91,88}                         & {86,72}                         & {49,74}                        & {88,06}                         & {100}                           & {76,52}                        \\
        {3}                           & {50}    & {90,84}                             & {90,93}                             & {52,78}                                   & \textbf{94,18}                  & {94,92}                         & {49,74}                        & {88,59}                         & {100}                           & {76,52}                        \\
        {3}                           & {100}   & {90,76}                             & {89,37}                             & {52,78}                                   & {92,8}                          & {94,1}                          & {49,74}                        & \textbf{91,84}                  & {100}                           & {76,52}                        \\
        {4}                           & {2}     & {92,11}                             & {94,86}                             & {52,04}                                   & {93,86}                         & {88,56}                         & {49,74}                        & {87,11}                         & {100}                           & {76,56}                        \\
        {4}                           & {10}    & {92,75}                             & {90,58}                             & {52,78}                                   & {93,71}                         & {95,05}                         & {49,74}                        & {89,89}                         & {100}                           & {76,52}                        \\
        {4}                           & {16}    & {94,14}                             & {\textbf{98,57}}                    & {52,78}                                   & {\textbf{95,23}}                & \textbf{96,14}                  & {49,74}                        & {88,06}                         & {100}                           & {76,52}                        \\
        {4}                           & {50}    & {93,32}                             & {95,66}                             & {52,78}                                   & {90,45}                         & {91,01}                         & {49,74}                        & {88,85}                         & {100}                           & {76,52}                        \\
        {4}                           & {100}   & {93,58}                             & {89,41}                             & {52,78}                                   & {93,19}                         & {94,66}                         & {49,74}                        & {86,98}                         & {100}                           & {76,52}                        \\
        {6}                           & {2}     & {92,94}                             & {93,39}                             & {52,04}                                   & {92,16}                         & {82,18}                         & {49,74}                        & {90,05}                         & {100}                           & {76,56}                        \\
        {6}                           & {10}    & {\textbf{94,23}}                    & {\textbf{98,78}}                    & {52,78}                                   & {92,75}                         & \textbf{96,79}                  & {49,74}                        & {87,67}                         & {100}                           & {76,52}                        \\
        {6}                           & {16}    & {91,32}                             & {96,96}                             & {52,78}                                   & {93,75}                         & {95,57}                         & {49,74}                        & {89,37}                         & {100}                           & {76,52}                        \\
        {6}                           & {50}    & {91,45}                             & {88,28}                             & {52,78}                                   & {86,24}                         & {91,71}                         & {49,74}                        & {88,32}                         & {100}                           & {76,52}                        \\
        {6}                           & {100}   & {92,45}                             & {94,92}                             & {52,78}                                   & {93,62}                         & {95,3}                          & {49,74}                        & {89,19}                         & {100}                           & {76,52}                        \\
        \bottomrule
    \end{tabular}
    \caption{TODO: caption}
    \label{TODO: label}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{ccc|ccc|ccc}
        \toprule
              &         &         & \multicolumn{3}{c}{\textbf{Dale-2}} & \multicolumn{3}{c}{\textbf{Dale-5}}                                                                             \\\cmidrule(lr){4-6}\cmidrule(lr){7-9}
        $|V|$ & $h_{s}$ & $h_{r}$ & \textbf{Acc.}                       & \textbf{word-by-word}               & \textbf{length} & \textbf{Acc.} & \textbf{word-by-word} & \textbf{length} \\\midrule
        {10}  & {10}    & {10}    & {22,9\%}                            & {62,8\%}                            & {1}             & {7,1\%}       & {40\%}                & {1}             \\
        {13}  & {10}    & {10}    & {22,8\%}                            & {62,9\%}                            & {0}             & {7,3\%}       & {38,7\%}              & {1}             \\
        {20}  & {10}    & {10}    & {24,6\%}                            & {64\%}                              & {1}             & {6,7\%}       & {38,7\%}              & {1}             \\
        {100} & {10}    & {10}    & {24,4\%}                            & {62\%}                              & {1}             & {7,8\%}       & {40\%}                & {1}             \\
        {100} & {100}   & {100}   & {21\%}                              & {62\%}                              & {1}             & {6,5\%}       & {37,8\%}              & {1}             \\
        \bottomrule
    \end{tabular}
    \caption{Results of the caption generator: $|V|$ are different vocabulary sizes and $h$ hidden sizes.}
    % SD: What is word-by-word?
    % DK: the same as in the caption generator with a single model (QUESTION)
    \label{tab:results_caption_generator_game}
\end{table}
